\section*{EXPERIENCE}

\noindent
\textbf{DB Max Limited}\\
\textit{Resource and development lead} \hfill 2024 - Ongoing
\begin{itemize}
    \item Jaret heads up the development and execution of IT based systems for use at events and in general management.
    \item Jaret managed the development and deployment of a brand new finish-line monitoring system.
    \item Jaret also helps with the design and analysis of marketing campaigns.
    \item Jaret's most recent project is an company wide inventory management system.
\end{itemize}

\noindent
\textbf{DB Max Limited}\\
\textit{Timer} \hfill 2024 - Ongoing
\begin{itemize}
    \item Jaret assists with chip timing systems: set up, monitoring and troubleshooting at mass sporting events with over 800 participants.
    \item Jaret additionally has operated and managed timing systems independently at events such as the 2024 OCR 100m championships.
    \item Jaret also undertakes construction and destruction of sporting events' venues.
\end{itemize}

\noindent
\textbf{Cardale Care}\\
\textit{Carer} \hfill 2022 - Ongoing
\begin{itemize}
    \item Jaret assists over ten adults with severe learning and physical disabilities in there own homes under the supported living scheme. This includes management of personal finances and time management in highly regulated tasks such as medication administrations.
\end{itemize}

\noindent
\textbf{Wiltshire Police DIIU}\\
\textit{Volunteer} \hfill 2019 - 2020 
\begin{itemize}
    \item Jaret as a voluntary member of the Wiltshire police Digital Investigations \& Intelligence Unit (DIIU) Jaret learned about the standardized cyber forensics techniques used in a modern police investigation this helped too expand his knowledge in specialist fields within cyber security.
    \item Jaret was allocated a case regarding a phishing email to investigate, Jaret was the lead on the investigation and had to plan and executed several procedures in order to produce any proof of potential malicious activity contained in the email.
\end{itemize}

\noindent
\textbf{BCH Camping and Leisure}\\
\textit{Sales assistant} \hfill 2018 – 2020
\begin{itemize}
    \item Jaret’s main role was to engage with customers and help guid them to the product that suits their needs best and to provide information on a range of products. Jaret would also oversee the process of preforming detailed stock checks to ensure that all digital databases are UpToDate. 
\end{itemize}

\noindent
\textbf{Zyko}\\
\textit{Systems Administrator} \hfill Aug 2016
\begin{itemize}
    \item During a period of two weeks Work Experience Jaret was responsible for making sure that IT support requests placed on the system were adhered to within a reasonable time frame. During this time, Jaret was also responsible for digitising the company’s asset records for future use and stock management.
\end{itemize}


\noindent
\textbf{Youth Action Wiltshire}\\
\textit{Youth Ambassador, Volunteer} \hfill 2016 – 2021
\begin{itemize}
    \item Jaret was responsible for assisting with group activities for children between twelve and seventeen years old these activities could involve upwards of a hundred people at a time.
\end{itemize}

